Web Service Community \\ Learning

### 2014-06-10 papers/webservice-coalition-learning/webservice_coalition_learning.tex
changes

\IEEEPARstart{O}{ver} the past years, online services have become part of many scalable business applications. The increasing reliance on online service providers has significantly influenced the way web services are engineered. Delivering high quality services considering the dynamic and unpredictable nature of the Internet is still a very critical and challenging issue. These services can be utilized on top of intelligent decision making agents in order to maximise gain by finding ways of providing services better satisfying end users. The recent developments are shifting web services from passive and individual components to autonomouse and group-based components where interaction, composition, and cooperation are the key challenges [refrences]. To this end the idea of \emph{community} of web services by gathering services having similar functionalies but distinct non-functional properties was developed [refrences].

Web service ocmmunities faciliate the discovery of web services and also provide services with better quality. These communities act as abstract web services, communicating with external entities via same standard protocols the normal web services employ. Users send their requests to the coordinators of those communities, which play the role of their representatives or access points. The community coordinator in this \emph{community centerilized} architecture is resposible for community management tasks such as verification of credentials of new web services before accepting them to join the community and also firing web services which do not add enough value to the community.

- We want to give full distributed control to web services as autonomouse agents and distribute the task of communty management among all web services and let them decide how to maximise their efficientcy and join and create communities.
- Let agents train and learn long term expectations of each action and group they can join with
- Web services cannot find the optimal solution in big space problem of many web services
- Add rationalism and less vague decisions

@@

\section{Related Work}\label{s:relatedwork}

>>>>

\IEEEPARstart{O}{ver} the past years, online services have become part of many scalable business applications. The increasing reliance on online service providers has significantly influenced the way web services are engineered. Delivering high quality services considering the dynamic and unpredictable nature of the Internet is still a very critical and challenging issue. These services can be utilized on top of intelligent decision making agents in order to maximize gain by finding ways of providing services better satisfying end users. The recent developments are shifting web services from passive and individual components to autonomous and group-based components where interaction, composition, and cooperation are the key challenges [references]. To this end the idea of \emph{community} of web services by gathering services having similar functionality but distinct non-functional properties was developed [references].

Web service communities facilitate the discovery of web services and also provide services with better quality. These communities act as abstract web services, communicating with external entities via same standard protocols the normal web services employ. Users send their requests to the coordinators of those communities, which play the role of their representatives or access points. The community coordinator in this \emph{community centralized} architecture is responsible for community management tasks such as verification of credentials of new web services before accepting them to join the community and also firing web services which do not add enough value to the community. Within communities,

Recent work have emphasized on motivation and benefits of communities of web services[references]. Communities of web services facilitate discovery of web services, improve the quality of service, and also help individual services find better market share and opportunities.

- We want to give full distributed control to web services as autonomous agents and distribute the task of community management among all web services and let them decide how to maximize their efficiency and join and create communities.
- Let agents train and learn long term expectations of each action and group they can join with
- Web services cannot find the optimal solution in big space problem of many web services
- Add rationalism and less vague decisions

@@

\section{Related Work}\label{s:related_work}

*******THIS ONE IS TEMPRORARY FROM PREVIOUS WORKS*******
In \cite{DBLP:journals/internet/BenatallahSD03}, Benatallah et al.
defined communities as \emph{Service Containers} which aggregate
substitutable web services providing a common functionality (same
set of operations). They abstracted \emph{Service Containers} as
web services which are created, advertised, discovered and invoked
just as elementary web services. The \emph{Container} is
considered as a manager which is responsible for web service
selection upon receiving a request on run-time. The authors have
proposed a scoring service based on non-functional requirements of
the request and web service capabilities to dynamically chose the
web service to perform the requested task. A similar concept was
proposed by Maamar et al. in
\cite{DBLP:journals/ijebr/MaamarSTBB09}. The authors introduced
web service communities as a collection of web services with a
common functionality but different QoS properties. A community
manager, upon receiving a request, delegates the request to one of
its current members. The choice is based on the performance
history and quality metrics of each web service. The authors have
proposed an efficient global web service selection algorithm in
order to approach quality constraints and preferences for
composite services which require aggregation of different types of
services to satisfy the user.

Benslimane et al. \cite{Liris-2770} have proposed a multi-layer
approach grouping similar Web services into communities and having
an interface implemented as an abstract web service for accessing
the community on top of the community layer. The interactions
between composite, management and community layers and the
bindings are performed by a generic driver called Open Software
Connectivity (OSC).

In \cite{managing-hela-jalel}, Limam and Akaichi have proposed web
service communities with centralized access across distributed web
services. They have proposed a framework for web service
management, query resolution among communities and a query caching
mechanism executed by the manager to improve the performance of
query resolution process among many distributed communities. The
key idea is to cache previous computed results for answering
future queries.

Maamar et al. initially in \cite{conf/webist/MaamarLBTS07} and
then comprehensively in \cite{DBLP:journals/ijebr/MaamarSTBB09}
proposed an architecture utilizing \emph{Contract-Net} protocol
for engineering task distribution within communities of web
services. The protocol is centrally executed by the community
manager. This architecture has been further developed in
\cite{CSTintercommunity, conf/IEEEscc/BenharrefSBB11,
conf/IEEEscc/KhosravifarBMMT10, conf/aina/LimTM11}. Two types of
roles have been distinguished for community members: masters and
slaves. Master web services and community managers that lead
communities and are responsible for membership management. They
can invite and convince slave web services to join the community,
and attract new slave web services to their communities by
awarding them better payoff. Moreover, they can eject some slave
members from the community to improve its overall reputation if
these members are misbehaving or cannot provide the promised QoS.

In \cite{Medjahed05adynamic}, Medjahed and Bouguettaya have
developed a community as a ``cluster'' that groups Web services
based on a specific area of interest. All web services in a given
community share the same functionality. These communities are
created by \emph{third party community providers} which use the
\emph{community ontology} as a template and define a set of
operations that all web services within a community should
provide. Using semantic analysis on web service operations, web
services either find and join a community with similar
functionality or create a new operation description for a new
community. The authors have described the concept of
\emph{community agents} associated to \emph{community providers}.
A community agent is responsible, among other things, of the
registration of services with the community. An example of a
community that provides health care services to senior citizens
has been used. In this example, a governmental entity is needed to
check the health care standards used by the members before
authorizing them to be part of the community. Such a central
entity is represented by the community agent. Thus, community
agents are playing the role of community managers. In a close work
\cite{Zeng:2003:QDW:775152.775211}, Zeng et al. have described a
global planning selection algorithm and a delegation algorithm to
be run when a request to execute an operation is received by the
community. This needs a central entity to run those algorithms.
Such entity plays the same role as the community coordinator or
manager.

Most of the recent work on communities of services are either
user-centric and focus on user satisfaction
\cite{Chun02user-centricperformance} or system-centric and focus
on the whole system throughput, performance and utilization. There
are many contributions in distributed, grid, cluster and cloud
services which are system-centric. However, in real world
environments and applications, both users and service providers
are self-interested agents, aiming to maximize their own profit.
In those environments, both parties (users and services) will
collaborate as long as they are getting more benefits and payoff.

In this direction, recently \cite{DBLP:conf/IEEEscc/LimTMB12,
DBLP:conf/IEEEscc/KhosravifarABT11, 10.1109/TSC.2012.12} proposed
mechanisms to help users and services maximize their gain. A
two-player non-cooperative game between web services and community
master was introduced in
\cite{DBLP:conf/IEEEscc/KhosravifarABT11}. In this game-theoretic
model, the strategies available to a web service when facing a new
community are requesting to join the community, accepting the
master's invitation to join the community, or refusing the
invitation to join. The set of strategies for communities are
inviting the web service or refusing the web service's join
request. Based on their capacity, market share and reputation, the
two players have different sets of utilities over the strategy
profiles of the game. The main limits of this game model are: 1)
its consideration of only three quality parameters, while the
other factors are simply ignored; and 2) the non-consideration of
the web services already residing within the community. The game
is only between the community master and the new web service, and
the inputs from all the other members and their influence on the
master's decision are simply ignored. The consideration of those
inputs and this influence factor is a significant issue as
existing web services can lose utility or payoff because of the
new member, which can result in an unhealthy and unstable group.
The problem comes from the fact that the existing members should
collaborate with the new web services, so probably their
performance as a group can suffer. Existing members may even
deviate and try to join other communities if they are unsatisfied.
Those considerations of forming stable and efficient coalitions
are the main contributions of our paper.

In \cite{DBLP:conf/IEEEscc/LimTMB12}, a 3-way satisfaction approach
for selecting web services has been proposed. In this approach,
the authors proposed a web service selection process that the
community masters can use. The approach considers the efficiency
of all the three involved parties, namely users, web services and
communities. In this work, it is shown how the gains of these
parties are coupled together using a linear optimization process.
However, the optimization problem in this solution tends to
optimize some parameters considering all web services regardless
of their efficiency and contribution to the community's welfare.
Moreover, there are no clear thresholds for accepting or rejecting
new web services. The solution of the optimization problem could,
for instance, suggest web services already residing within the
community to increase or decrease their capacity to cover up the
weakness of other parties in the system. However, a high
performing web service could deviate anytime it finds itself
unsatisfied within the community instead of adjusting its service
parameters.

In \cite{10.1109/TSC.2012.12}, a cooperative scheme among
autonomous web services based on coalitional game theory has been
introduced. The authors have proposed an interesting algorithm to
reach individually stable coalition partition for web services in
order to maximize their efficiency. The communities choose new web
services on the promise that it would benefit the community
without decreasing any other web service's income. In the proposed
model, the worth of community is evaluated with high emphasis on
the availability metric and considering price and cost values
only. The community structure is based on a coordination chain,
where a web service is considered as a \emph{primary} web service
and the community task-distribution method initially invokes the
primary web service and only if the primary web service is
unavailable, the method invokes the next backup web services as
they are ordered in the coordination chain. We believe that this
coordination chain limits the cooperation power as it introduces a
sort of hierarchy. However, in pure and open cooperative models,
such as the one we propose in this paper, active cooperation
activities engaging simultaneously many agents so that they can
perform the tasks more efficiently are being used. Moreover, if
the availability is high, which is the case nowadays with the
recent advancements in cloud and hardware infrastructures, the
backup web services will end-up having a very low chance of
getting jobs, especially the ones further in the chain. This will
results in a considerable waste of web services capabilities.
*******THIS ONE IS TEMPRORARY FROM PREVIOUS WORKS*******
